Report on Certificate Tools

### 2016-09-12 TEX/draft.tex
Almost final Keytool text, only need to write commands for signed chain, GnuPG will be added soon, just need to be sure about everything.

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|}
\hline
                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
Keygen                  & JKS    & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

@@

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keygen                 &                                                                      &                             &                             &                             &                             &                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keygen                 &                               &                                          &                                                &                                            &                                                                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-2}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  &                                  &                             &                                         &                                                                  \\ \hline
                        &                                  &                             &                                         &                                                                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\chapter{Keygen}

@@

Viewing Public key part of certificate is not availiable in keytool.
  \subsection{License}
%need to ask some things

@@

      \paragraph{Specify Type}
With keytool you can make a self-signed CA certificate by using \verb+-ext ca:true+ option.

      \paragraph{Specify path length}
Specifying of path length is possible while making a certificate by using  \\
\verb+-ext pathlen:[int path length]+ option.

@@

    \subsubsection{Certificate Signing Request signing}
Keytool cannot be used to sign Certificate Signing Request. It can import certificate signed by CA but as a standalone tool cannot sign a CSR with a CA cert.
%I'm sorry but i haven't found a way to sign a CSR with CA cert with keytool alone

@@

    \subsubsection{Support for Cryptographic Service Provider}
Support for Cryptographic service provider is native but there is need for a definition of path where the CSR is located.
\begin{verbatim}
-storetype [keystore_type_of_implementation]
-provider [provider_implementation_name]
-providerpath [provider_implementation_type]
\end{verbatim}
%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found

@@

>>>>

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{General}                                                             \\ \cline{2-5} 
\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & Both             \\ \hline
Keygen                  & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & Both             \\ \hline
GnuPG                   &        &                                                    &         &                  \\ \hline
Keystore Explorer       &        &                                                    &         &                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\subsection{Operating Systems}
In this part the Operating System where the tool is imported is defined. Both means that it is implemented under UNIX like systems and Windows systems. Otherwise the Operating System is defined (Windows | UNIX).

@@

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
Keystore explorer      &                                                                      &                             &                             &                             &                             &                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keygen                 & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
Keystore explorer      &                               &                                          &                                                &                                            &                                                                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5} 
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
Keystore explorer       &                                  &                             &                                         &                                                                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\chapter{Keytool}

@@

Viewing Public key part of certificate is not availiable in keytool.
  \subsection{License}
Keytool is free to use in production code and is licensed under Apache Licence Version 2.0. For more detailed description look at http://www.apache.org/licenses/LICENSE-2.0.txt

@@

      \paragraph{Specify Type}
With keytool you can make a self-signed CA certificate by using \verb+-ext BC=ca:[true|false]+ option.

      \paragraph{Specify path length}
Specifying of path length is possible while making a certificate by using  \\
\verb+-ext BC=pathlen:[int path length]+ option.

@@

    \subsubsection{Certificate Signing Request signing}
Keytool can sign a CSR if a CA certificate and a keystore containing it are avaliable:
\begin{verbatim}
keytool -gencert -rfc -keystore [root_keystore.jks] \
        -alias [CA_cert_alias] -storepass [store_password] \
        -infile [CSR_file.csr] -validity <int_length> \
        -outfile [output_certificate.crt] -ext BC=ca:[true|false] \
        -ext SAN=ip:<IP_address>,dn:<DNS_address> 
\end{verbatim}

@@

    \subsubsection{Support for Cryptographic Service Provider}
Support for Cryptographic Service Provider is native but there is need for a definition of path where the CSP is located.
\begin{verbatim}
-storetype [keystore_type_of_implementation]
-provider [provider_implementation_name]
-providerpath [provider_implementation_type]
\end{verbatim}
%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found

@@

\chapter{GnuPG}

\chapter{Keystore Explorer}
